\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}

\title{Formally Verified Concurrent Cluster Provisioning:\\
Readiness Barriers and Scale-Tolerant Convergence Policies}
\author{Benjamin Arntzen \\ \texttt{team@riff.cc} \\ Riff Labs}
\date{Draft --- \today}

\begin{document}
\maketitle

\begin{abstract}
[TODO] Concurrent JIT provisioning of a cluster of hosts must fan out imaging,
gate convergence behind a readiness barrier, and tolerate node failure at scale.
We model this protocol as a state machine, prove its safety and liveness
properties in Lean 4, validate the scale-tolerant convergence policies
(strict-all / percentage-threshold / max-failures) under randomized failure via a
Python simulator, and present the verified design implemented in Rust as the
jetpack automation engine.
\end{abstract}

\section{Introduction}
[TODO] Provisioning at scale; failure as a forcing function; the correctness
pitfalls (deadlock on an errored host, races across the barrier, quorum math).

\section{The Protocol}
[TODO] State machine: host $\in$ \{Provisioning, Ready, Failed\}; phase $\in$
\{Imaging, Barrier, Converge\}; transitions \texttt{fan\_out} /
\texttt{host\_ready} / \texttt{host\_fail} / \texttt{policy\_check} /
\texttt{proceed}.

\section{Formalization in Lean 4}
[TODO] Layer by layer: L0 strict-all barrier, L1 \%-threshold, L2 max-failures, L3
composition with the play-level \texttt{!wait\_for\_others} /
\texttt{!assert} / \texttt{!fail} primitives.

\section{Properties and Proofs}
[TODO] Safety: $proceed \Rightarrow policy\_satisfied$. Liveness: the barrier
always resolves. Policy correctness per layer.

\section{Scale Simulation}
[TODO] Python fuzz at $10^4$ hosts; randomized failure injection; property-based
assertions.

\section{Implementation}
[TODO] Rust in jetpack: parallel provision fan-out + readiness state, composed
with the existing play modules.

\section{Related Work}
[TODO] Terraform, Ansible \texttt{serial} / \texttt{max\_fail\_percentage}, formal
methods in infrastructure provisioning.

\section{Conclusion}
[TODO]

\end{document}
